Analysis

### 2020-04-06 production/prod_analysis-cfa.rmd

---
title: "Analysis"
date: "`r format(Sys.time(), '%d %B, %Y')`"
css: "../input/bib/style.css"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    toc_depth: 4
    code_folding: "hide"
editor_options: 
  chunk_output_type: console
---

# Análisis PPM-S

# Wave 01

```{r eval=FALSE, include=FALSE}
rmarkdown::render(input = "production/analysis-cfa.Rmd",output_format = "html_document")
```

@@

```{r}
library(sjPlot)
library(dplyr)
library(lavaan)
library(stargazer)
library(corrplot)
library(psych)
library(knitr)
library(kableExtra)
```

```{r}
data01 <- sjlabelled::read_spss(path = "input/data/original/Estudio_3_ola1.sav",verbose = FALSE)

@@

## Version 01: Fixed order by perception / preferences (N=`r dim(dat01)[1]`)

1. Percepcion esfuerzo
2. Percepcion talento
3. Percepcion familia rica
4. Percepcion redes
5. Preferencia esfuerzo
6. Preferencia talento
7. Preferencia familia rica
8. Preferencia redes

```{r echo=FALSE,results='asis'}
stargazer(dat01,type = "html")
```

```{r correlacion v01}
cor01<-polychoric(dat01)
corrplot(cor01$rho,method = "color" ,type = "upper", order = "hclust", tl.col = "black", tl.srt = 45,addCoef.col = "black",diag = FALSE)
```

```{r}
model01 <- '
perc_merit=~meritv01_perc_effort+meritv01_perc_talent 
perc_nmerit=~meritv01_perc_wpart+meritv01_perc_netw  
pref_merit=~meritv01_pref_effort+meritv01_pref_talent 
pref_nmerit=~meritv01_pref_wpart+meritv01_pref_netw'

fit1_c <- cfa(model = model01,data = dat01,estimator="MLR") # Continuo/ estimador ML Robust

@@

#---------------------------------------------------#
# #summary(fit1_c,standardized=TRUE, fit.measures=TRUE)}
fitmeasures(fit1_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]
semPlot::semPaths(object = fit1_c,what = "std",thresholds = FALSE, intercepts = FALSE,fade=FALSE, curve = 1.5)

# #summary(fit1_o,standardized=TRUE, fit.measures=TRUE)
fitmeasures(fit1_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]
semPlot::semPaths(object = fit1_o,what = "std",thresholds = FALSE, intercepts = FALSE,fade=FALSE, curve = 1.5)
```

> *#summary*: good fit, heywood case item 8.

## Version 02: Fixed order, by topic (N=`r dim(dat02)[1]`)

1. Percepcion esfuerzo
2. Preferencia esfuerzo
3. Percepcion talento
4. Preferencia talento
5. Percepcion familia rica
6. Preferencia familia rica
7. Percepcion redes
8. Preferencia redes

```{r echo=FALSE,results='asis'}
stargazer(dat02,type = "html")
```

```{r}
cor02<-polychoric(dat02)
corrplot(cor02$rho,method = "color", type = "upper", order = "hclust", tl.col = "black", tl.srt = 45,addCoef.col = "black",diag = FALSE)
```

```{r,results='hold'}
model02 <- '
perc_merit=~meritv02_perc_effort+meritv02_perc_talent 
perc_nmerit=~meritv02_perc_wpart+meritv02_perc_netw  
pref_merit=~meritv02_pref_effort+meritv02_pref_talent 
pref_nmerit=~meritv02_pref_wpart+meritv02_pref_netw'

fit2_c <- cfa(model = model02,data = dat02,estimator="MLR") # Continuo/ estimador ML Robust

fit2_o <- cfa(model = model02,data = dat02,ordered = c("meritv02_perc_effort","meritv02_perc_talent",
                                                     "meritv02_perc_wpart","meritv02_perc_netw",
                                                     "meritv02_pref_effort","meritv02_pref_talent",
                                                     "meritv02_pref_wpart","meritv02_pref_netw"))

#---------------------------------------------------#
#summary(fit2_c,standardized=TRUE, fit.measures=TRUE)
fitmeasures(fit2_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]
semPlot::semPaths(object = fit2_c,what = "std",thresholds = FALSE, intercepts = FALSE,fade=FALSE, curve = 1.5)

#summary(fit2_o,standardized=TRUE, fit.measures=TRUE)
fitmeasures(fit2_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]
semPlot::semPaths(object = fit2_o,what = "std",thresholds = FALSE, intercepts = FALSE,fade=FALSE, curve = 1.5)
```
> **NOTA**: bad fit, heywood en estimación DWLS

## Version 03: Random order (N=`r dim(dat03)[1]`)

```{r echo=FALSE,results='asis'}
stargazer(dat03,type = "html")
```

```{r}
cor03<-polychoric(dat03)
corrplot(cor03$rho,method = "color", type = "upper", order = "hclust", tl.col = "black", tl.srt = 45,addCoef.col = "black",diag = FALSE)
```

@@

fit3_c <- cfa(model = model03,data = dat03,estimator="MLR",std.lv=FALSE) # Continuo/ estimador ML Robust

fit3_o <- cfa(model = model03,data = dat03,ordered = c("meritv03_perc_effort","meritv03_perc_talent",
                                                       "meritv03_perc_wpart","meritv03_perc_netw",
                                                       "meritv03_pref_effort","meritv03_pref_talent",
                                                       "meritv03_pref_wpart","meritv03_pref_netw"),std.lv=FALSE)
#---------------------------------------------------#
#summary(fit3_c,standardized=TRUE, fit.measures=TRUE)
fitmeasures(fit3_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]
semPlot::semPaths(object = fit3_c,what = "std",thresholds = FALSE, intercepts = FALSE,fade=FALSE, curve = 1.5)

#summary(fit3_o,standardized=TRUE, fit.measures=TRUE)
fitmeasures(fit3_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]
semPlot::semPaths(object = fit3_o,what = "std",thresholds = FALSE, intercepts = FALSE,fade=FALSE, curve = 1.5)
```

> **NOTA**: fit not very goood (RMSEA .7), no heywood. Try tau-equivalence

@@

fit3_c.tau <- cfa(model = model03.tau,data = dat03,estimator="MLR",std.lv=FALSE) # Continuo/ estimador ML Robust

fit3_o.tau <- cfa(model = model03.tau,data = dat03,ordered = c("meritv03_perc_effort","meritv03_perc_talent",
                                                               "meritv03_perc_wpart","meritv03_perc_netw",
                                                               "meritv03_pref_effort","meritv03_pref_talent",
                                                               "meritv03_pref_wpart","meritv03_pref_netw"), std.lv=FALSE)
#---------------------------------------------------#
#summary(fit3_c.tau,standardized=TRUE, fit.measures=TRUE)
fitmeasures(fit3_c.tau)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]
semPlot::semPaths(object = fit3_c.tau,what = "std",thresholds = FALSE, intercepts = FALSE,fade=FALSE, curve = 1.5)

#summary(fit3_o,standardized=TRUE, fit.measures=TRUE)
fitmeasures(fit3_o.tau)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]
semPlot::semPaths(object = fit3_o.tau,what = "std",thresholds = FALSE, intercepts = FALSE,fade=FALSE, curve = 1.5)
```

```{r}
rbind(fitmeasures(fit3_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
      fitmeasures(fit3_o.tau)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")])
anova(fit3_o,fit3_o.tau)
```

> **NOTA:** El modelo con igualdad de cargas factoriales no deteriora significativamente el ajuste del modelo.

## Version 04: muestra completa (N=`r dim(dat04)[1]`)

```{r echo=FALSE,results='asis'}
stargazer(select(dat04,perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw),
          type = "html")
```

```{r}
cor04<-polychoric(select(dat04,perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw))
corrplot(cor04$rho, method="color",type = "upper", order = "hclust", tl.col = "black", tl.srt = 45,addCoef.col = "black",diag = FALSE)
```

@@

fit4_c <- cfa(model = model04,data = dat04,estimator="MLR",std.lv=FALSE) # Continuo/ estimador ML Robust

fit4_o <- cfa(model = model04,data = dat04,ordered = c("perc_effort","perc_talent",
                                                       "perc_wpart","perc_netw",
                                                       "pref_effort","pref_talent",
                                                       "pref_wpart","pref_netw"),std.lv=FALSE)
#---------------------------------------------------#
#summary(fit4_c,standardized=TRUE, fit.measures=TRUE)
fitmeasures(fit4_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]
semPlot::semPaths(object = fit3_c,what = "std",thresholds = FALSE, intercepts = FALSE,fade=FALSE,curve = 2)

#summary(fit4_o,standardized=TRUE, fit.measures=TRUE)
fitmeasures(fit4_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]
semPlot::semPaths(object = fit3_o,what = "std",thresholds = FALSE, intercepts = FALSE,fade=FALSE,curve = 2)
```

### Resumen ajuste ola 01

```{r}
sum_fit<- bind_rows(fitmeasures(fit1_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit1_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit2_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit2_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit3_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit3_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit4_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit4_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")])
sum_fit$mod <- c("Modelo 1","Modelo 1","Modelo 2","Modelo 2","Modelo 3","Modelo 3","Modelo 4","Modelo 4")
sum_fit$est <- c("Continuo","Ordinal","Continuo","Ordinal","Continuo","Ordinal","Continuo","Ordinal")
sum_fit <- select(sum_fit,mod,est,everything())

kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Resumen estadísticos de ajuste ola 1") %>% kable_styling(full_width = F) %>% 
  collapse_rows(columns = 1,valign = "middle")  %>% 
  footnote(number = c("Modelo 1: fixed order by percepction/preference", 
                      "Modelo 2: fixed order by topic (i.e: effort)", 
                      "Modelo 3: Randomized order",
                      "Modelo 4: Complete sample"))
```

## Análisis por Grupos múltiples

@@

fit4_c_mg <- cfa(model = model04,data = dat04,estimator="MLR",std.lv=FALSE,group = "grupo") # Continuo/ estimador ML Robust

fit4_o_mg <- cfa(model = model04,data = dat04,ordered = c("perc_effort","perc_talent",
                                                       "perc_wpart","perc_netw",
                                                       "pref_effort","pref_talent",
                                                       "pref_wpart","pref_netw"),std.lv=FALSE, group = "grupo")
#---------------------------------------------------#
#summary(fit4_c_mg,standardized=TRUE, fit.measures=TRUE)
fitmeasures(fit4_c_mg)[c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]
semPlot::semPaths(object = fit4_c_mg,what = "std",thresholds = FALSE, intercepts = FALSE, fade=FALSE, curve=2)

#summary(fit4_o_mg,standardized=TRUE, fit.measures=TRUE)
fitmeasures(fit4_o_mg)[c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]
semPlot::semPaths(object = fit4_o_mg,what = "std",thresholds = FALSE, intercepts = FALSE,fade=FALSE, curve=2)
```

Cosas por probar:

* V01+V02: cargas y fit
* V01+V03: cargas y fit
* V02+V03: cargas y fit

# Modelo Factorial de Segundo Orden:

## a. Factor de segundo orden por Percepción y Preferencia

@@

#---------------------------------------------------#
#summary(fit4a_c,standardized=TRUE, fit.measures=TRUE)
fitmeasures(fit4a_c)[c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]
semPlot::semPaths(object = fit4a_c,what = "std",thresholds = FALSE, intercepts = FALSE, fade=FALSE,curve=2)

#summary(fit4b_c,standardized=TRUE, fit.measures=TRUE)
fitmeasures(fit4b_c)[c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]
semPlot::semPaths(object = fit4b_c,what = "std",thresholds = FALSE, intercepts = FALSE, fade=FALSE,curve=2)
```

> **NOTA:** Cargas factoriales de segundo orden son bajas. El ajuste del modelo no es bueno.

## b. Factor de segundo orden por Meritocracia y No Meritocracia

@@

#---------------------------------------------------#
# #summary(fit4b_c,standardized=TRUE, fit.measures=TRUE)
# fitmeasures(fit4b_c)[c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]
# semPlot::semPaths(object = fit4b_c,what = "std",thresholds = FALSE, intercepts = FALSE, fade=FALSE, curve=2)

#summary(fit4b_o,standardized=TRUE, fit.measures=TRUE)
fitmeasures(fit4b_o)[c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]
semPlot::semPaths(object = fit4b_o,what = "std",thresholds = FALSE, intercepts = FALSE, fade=FALSE, curve=2)
```

> **NOTA:** El modelo estimado con MLR con factores de segundo orden "meritocracia/ no meritocracia" no converge. EL modelo estimado a través de DWLS converge, posee cargas muy bajas y una muy alta (merit~pref_merit). Fit es malo (RMSEA >.10)

# Wave 02

@@

## ATE indicadores meritocracia

>>>>

---
title: "Analysis"
date: "`r format(Sys.time(), '%d %B, %Y')`"
css: "../input/bib/style.css"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: "hide"
editor_options: 
  chunk_output_type: console
---

# Analysis PPM-S

This section, documents all the procedures related to the data analysis and measurement models.

# Wave 01 {.tabset .tabset-fade .tabset-pills}

```{r eval=FALSE, include=FALSE}
rmarkdown::render(input = "production/prod_analysis-cfa.Rmd",output_format = "html_document")
```

@@

**Libraries**
```{r}
library(sjPlot)
library(dplyr)
library(lavaan)
library(stargazer)
library(corrplot)
library(psych)
library(knitr)
library(kableExtra)
```

**Load data**
```{r}
data01 <- sjlabelled::read_spss(path = "input/data/original/Estudio_3_ola1.sav",verbose = FALSE)

@@

---

**Modality**

Each group correspond to the application modality of the scale.

1. **Version 01:** Fixed order by perception / preferences (N=`r dim(dat01)[1]`)

2. **Version 02:** Fixed order, by topic (N=`r dim(dat02)[1]`)

3.  **Version 03:** Random order (N=`r dim(dat03)[1]`)

4. **Version 04:** Complete sample (N=`r dim(dat04)[1]`)

## Version 01 (N=`r dim(dat01)[1]`){.tabset}

| Spanish (original)          | English (translated)   |
|-----------------------------|------------------------|
| 1. Percepción esfuerzo      | Perception effort      |
| 2. Percepción talento       | Perception talent      |
| 3. Percepción familia rica  | Perception rich family |
| 4. Percepción redes         | Perception networks    |
| 5. Preferencia esfuerzo     | Preference effort      |
| 6. Preferencia talento      | Preference talent      |
| 7. Preferencia familia rica | Preference rich family |
| 8. Preferencia redes        | Preference networks    |
Table: Mode 01: Fixed order by perception

```{r echo=FALSE,results='asis'}
stargazer(dat01,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2,
          covariate.labels = c("1. pc.effort", "2. pc.talent","3. pc.wpart","4. pc.netw","5. pf.effort","6. pf.talent","7. pf.wpart", "8. pf.netw"))

```

```{r correlacion v01}
cor01<-polychoric(dat01)
rownames(cor01$rho) <- c("1. pc_effort", "2. pc_talent","3. pc_wpart","4. pc_netw","5. pf_effort","6. pf_talent","7. pf_wpart", "8. pf_netw")
colnames(cor01$rho) <- c("(1)", "(2)","(3)","(4)","(5)","(6)","(7)", "(8)")
corrplot(cor01$rho,method = "color" ,type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

```{r}
model01 <- 'perc_merit=~meritv01_perc_effort+meritv01_perc_talent
            perc_nmerit=~meritv01_perc_wpart+meritv01_perc_netw
            pref_merit=~meritv01_pref_effort+meritv01_pref_talent
            pref_nmerit=~meritv01_pref_wpart+meritv01_pref_netw'

fit1_c <- cfa(model = model01,data = dat01,estimator="MLR") # Continuous/ estimator ML Robust

@@

#---------------------------------------------------#
cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fit1_c) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),y = standardizedsolution(fit1_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames, caption = "Factor loadings")
```

> **NOTE**: good fit, heywood case item 8.

## Version 02  (N=`r dim(dat02)[1]`)

| Spanish (original)          | English (translated)   |
|-----------------------------|------------------------|
| 1. Percepción esfuerzo      | Perception effort      |
| 2. Preferencia esfuerzo     | Preference effort      |
| 3. Percepción talento       | Perception talent      |
| 4. Preferencia talento      | Preference talent      |
| 5. Percepción familia rica  | Perception rich family |
| 6. Preferencia familia rica | Preference rich family |
| 7. Percepción redes         | Perception networks    |
| 8. Preferencia redes        | Preference networks    |
Table: Mode 02: Fixed order, by topic.

```{r echo=FALSE,results='asis'}
stargazer(dat02,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2,
          covariate.labels = c("1. pc.effort","2. pf.effort","3. pc.talent","4. pf.talent","5. pc.wpart","6. pf.wpart","7. pc.netw","8 pc.netw"))
```

```{r}
cor02<-polychoric(dat02)
rownames(cor02$rho) <-c("1. pc_effort", "2. pc_talent","3. pc_wpart","4. pc_netw","5. pf_effort","6. pf_talent","7. pf_wpart", "8. pf_netw")
colnames(cor02$rho) <-c("(1)", "(2)","(3)","(4)","(5)","(6)","(7)", "(8)")
corrplot(cor02$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

```{r,results='hold'}
model02 <- 'perc_merit=~meritv02_perc_effort+meritv02_perc_talent
            perc_nmerit=~meritv02_perc_wpart+meritv02_perc_netw
            pref_merit=~meritv02_pref_effort+meritv02_pref_talent
            pref_nmerit=~meritv02_pref_wpart+meritv02_pref_netw'

fit2_c <- cfa(model = model02,data = dat02,estimator="MLR") # Continuous/ estimator ML Robust

fit2_o <- cfa(model = model02,data = dat02,ordered = c("meritv02_perc_effort","meritv02_perc_talent",
                                                       "meritv02_perc_wpart"  ,"meritv02_perc_netw",
                                                       "meritv02_pref_effort" ,"meritv02_pref_talent",
                                                       "meritv02_pref_wpart"  ,"meritv02_pref_netw"))

#---------------------------------------------------#
cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fit2_c) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),y = standardizedsolution(fit2_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames, caption = "Factor loadings")
```
> **NOTE**: bad fit, heywood case using DWLS

## Version 03 (N=`r dim(dat03)[1]`)

| Spanish (original)          | English (translated)   |
|-----------------------------|------------------------|
| Orden aleatorio             | Randomized order       |

Table: Mode 03: Randomized order.

```{r echo=FALSE,results='asis'}
stargazer(dat03,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2,
          covariate.labels = c("1. pc.effort", "2. pc.talent","3. pc.wpart","4. pc.netw","5. pf.effort","6. pf.talent","7. pf.wpart", "8. pf.netw"))
```

```{r}
cor03<-polychoric(dat03)
rownames(cor03$rho) <-c("1. pc_effort", "2. pc_talent","3. pc_wpart","4. pc_netw","5. pf_effort","6. pf_talent","7. pf_wpart", "8. pf_netw")
colnames(cor03$rho) <-c("(1)", "(2)","(3)","(4)","(5)","(6)","(7)", "(8)")
corrplot(cor03$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

@@

fit3_c <- cfa(model = model03,data = dat03,estimator="MLR",std.lv=FALSE) # Continuous/ estimator ML Robust

fit3_o <- cfa(model = model03,data = dat03,ordered = c("meritv03_perc_effort","meritv03_perc_talent",
                                                       "meritv03_perc_wpart","meritv03_perc_netw",
                                                       "meritv03_pref_effort","meritv03_pref_talent",
                                                       "meritv03_pref_wpart","meritv03_pref_netw"),std.lv=FALSE)
#---------------------------------------------------#
cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fit3_c) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),y = standardizedsolution(fit3_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames, caption = "Factor loadings")
```

> **NOTE**: fit not very goood (RMSEA .7), no heywood. Try tau-equivalence

### Tau-equivalence

@@

fit3_c.tau <- cfa(model = model03.tau,data = dat03,estimator="MLR",std.lv=FALSE) # Continuous/ estimator ML Robust

fit3_o.tau <- cfa(model = model03.tau,data = dat03,ordered = c("meritv03_perc_effort","meritv03_perc_talent",
                                                               "meritv03_perc_wpart","meritv03_perc_netw",
                                                               "meritv03_pref_effort","meritv03_pref_talent",
                                                               "meritv03_pref_wpart","meritv03_pref_netw"), std.lv=FALSE)
#---------------------------------------------------#
cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fit3_c.tau ) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),y = standardizedsolution(fit3_o.tau) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames)
```

```{r}
kable(rbind(Ordinal    =fitmeasures(fit3_o    )[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
            Ordinal.tau=fitmeasures(fit3_o.tau)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]),
      format = "markdown",
      digits = 3, caption = "Fit tau-equivalence")
kable(anova(fit3_o,fit3_o.tau),
      format = "markdown",
      digits = 3)
```

<!-- > **NOTE:** El modelo con igualdad de cargas factoriales (en Percepción meritocracia) no deteriora significativamente el ajuste del modelo. -->

> **NOTE:** The model with equal factor loadings (in Meritocracy Perception) does not significantly deteriorate the model fit.

## Version 04 (N=`r dim(dat04)[1]`)

| Spanish (original)                           | English (translated)                 |
|----------------------------------------------|--------------------------------------|
| Orden fijo, según percepción/preferencia     | Fixed order, by perception/preference|
| Orden fijo, por tópico                       | Fixed order, by topic.               |
| Orden aleatorizado                           | Randomized order                     |
Table: Mode 04: Complete sample

```{r echo=FALSE,results='asis'}
stargazer(select(dat04,perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw),
          type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2,
          covariate.labels = c("1. pc.effort", "2. pc.talent","3. pc.wpart","4. pc.netw","5. pf.effort","6. pf.talent","7. pf.wpart", "8. pf.netw"))
```

```{r}
cor04<-polychoric(select(dat04,perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw))
rownames(cor04$rho) <-c("1. pc_effort", "2. pc_talent","3. pc_wpart","4. pc_netw","5. pf_effort","6. pf_talent","7. pf_wpart", "8. pf_netw")
colnames(cor04$rho) <-c("(1)", "(2)","(3)","(4)","(5)","(6)","(7)", "(8)")
corrplot(cor04$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

@@

fit4_c <- cfa(model = model04,data = dat04,estimator="MLR",std.lv=FALSE) # Continuous/ estimator ML Robust

fit4_o <- cfa(model = model04,data = dat04,ordered = c("perc_effort","perc_talent",
                                                       "perc_wpart","perc_netw",
                                                       "pref_effort","pref_talent",
                                                       "pref_wpart","pref_netw"),std.lv=FALSE)
#---------------------------------------------------#
cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fit4_c ) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),y = standardizedsolution(fit4_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames, caption = "Factor loadings")
```

# Summary fit indices wave 01

```{r}
sum_fit<- bind_rows(fitmeasures(fit1_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit1_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit2_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit2_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit3_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit3_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit4_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit4_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")])
sum_fit$mod <- c("Model 1","Model 1","Model 2","Model 2","Model 3","Model 3","Model 4","Model 4")
sum_fit$est <- c("Continous","Ordinal","Continous","Ordinal","Continous","Ordinal","Continous","Ordinal")
sum_fit <- select(sum_fit,mod,est,everything())

sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Summary fit indices wave 01") %>%     kable_styling(full_width = F)  %>% 
      collapse_rows(columns = 1,valign = "middle")  %>%  
      footnote(number = c("Model 1: fixed order by percepction/preference", 
                          "Model 2: fixed order by topic (i.e: effort)", 
                          "Model 3: Randomized order",
                          "Model 4: Complete sample"));sumtable01

# Save sumamry table wave 01------------------------------#
# as_image(sumtable01,file = "output/sumtablew01.png")
save_kable(sumtable01,file = "output/tables/sumtablew01.html",self_contained = FALSE)
```

## Other analyses

### Multigroup CFA

* The group specification correspond to the application modality of the scale.

@@

fit4_c_mg <- cfa(model = model04,data = dat04,estimator="MLR",std.lv=FALSE,group = "grupo") # Continuous/ estimator ML Robust
fit4_o_mg <- cfa(model = model04,data = dat04,ordered = c("perc_effort","perc_talent",
                                                          "perc_wpart","perc_netw",
                                                          "pref_effort","pref_talent",
                                                          "pref_wpart","pref_netw"),std.lv=FALSE, group = "grupo")
#---------------------------------------------------#
kable(rbind(Continuous=fitmeasures(fit4_c_mg)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
            Ordinal=  fitmeasures(fit4_o_mg)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]),
      format = "markdown",digits = 3,caption = "Fit indices")

cnames <- c("Grupo","Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fit4_c_mg) %>% filter(op=="=~") %>% select(group,lhs,rhs,est.std),
                y = standardizedsolution(fit4_o_mg) %>% filter(op=="=~") %>% select(group,lhs,rhs,est.std),
                c("group","lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames,caption = "Factor loadings by group")
```

### Second order CFA

#### SO-CFA Perception and Preference

@@

#---------------------------------------------------#
kable(rbind(Continuous=fitmeasures(fit4a_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
            Ordinal= fitmeasures(fit4b_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]),
      format = "markdown",digits = 3)

cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fit4a_c) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
                y = standardizedsolution(fit4b_c) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
                c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames,caption = "Factor loadings")
```

<!-- > **NOTE:** Cargas factoriales de segundo orden son bajas. El ajuste del modelo no es bueno. -->

> **NOTE:** Second order factor loads are low. The fit of the model is not good.

#### SO-CFA Meritocratic y Non-meritocratic

@@

#---------------------------------------------------#
kable(rbind(Ordinal=fitmeasures(fit4b_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]),
      format = "markdown",digits = 3)

cnames <- c("Factor","Indicator","Loading (DWLS)")
kable(standardizedsolution(fit4b_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
      format = "markdown",digits = 2,col.names = cnames,caption = "Factor loadings")
```

<!-- > **NOTE:** El modelo estimado con MLR con factores de segundo orden "meritocracia/ no meritocracia" no converge. EL modelo estimado a través de DWLS converge, posee cargas muy bajas y una muy alta (merit~pref_merit). Fit es malo (RMSEA >.10) -->

> **NOTE:**  The model estimated with MLR with second order factors "meritocracy / non meritocracy" does not converge. The model estimated through DWLS converges, has very low loads and a very high one (merit ~ pref_merit). Fit is bad (RMSEA> .10)

# Wave 02 {.tabset .tabset-fade .tabset-pills}

Each sample correspond to one of the three conditions generated by the randomized assignment.

1. **Control group:** the group that has been assigned to the control group (placebo condition)

2. **Poverty condition sample** the group that has been assigned to the Poverty treatment condition.

3. **Inequality condition sample:** the group that has been assigned to the Inequality treatment condition.

4. **Complete sample:** Control, Poverty and Inequality treatment.

@@

**ATE on observed indicators**
